Species & genus plant classification with NEON hyperspectral data

### 2020-09-01 analysis/paper/paper.Rmd
adding gitignores to remove certain files from github

---
title: "Species & genus plant classification with NEON hyperspectral data"
author:
  - Victoria Scholl\thanks{maxwell.b.joseph@colorado.edu, Earth Lab, University of Colorado, Boulder, CO 80303, USA}
  - Maxwell B. Joseph\thanks{maxwell.b.joseph@colorado.edu, Earth Lab, University of Colorado, Boulder, CO 80303, USA}

@@

Here is a citation [@Marwick2017]

@@

@@

@@

### Colophon

This report was generated on `r Sys.time()` using the following computational environment and dependencies:

```{r colophon, cache = FALSE}
# which R packages and versions?
if ("devtools" %in% installed.packages()) devtools::session_info()
```

The current Git commit details are:

```{r}
# what commit is this file at? 
if ("git2r" %in% installed.packages() & git2r::in_repository(path = ".")) git2r::repository(here::here())  
```

>>>>

---
title: "Species & genus plant classification with NEON hyperspectral data"
author:
  - Victoria Scholl\thanks{victoria.scholl@colorado.edu, Earth Lab and Geography Dept., University of Colorado, Boulder, CO 80303, USA}
  - Maxwell B. Joseph\thanks{maxwell.b.joseph@colorado.edu, Earth Lab, University of Colorado, Boulder, CO 80303, USA}

@@

The National Ecological Observatory Network (NEON) is a valuable source of publicly available ecological data across the United States [@keller2008continental].

We have extracted all NEON AOP hyperspectral data for every mapped stem in NEON plots where field data and airborne remote sensing data were collected during the same year.

Here's the code to extract the spectra: [https://gist.github.com/mbjoseph/5c18781e508460e14f64193571b98b7d](https://gist.github.com/mbjoseph/5c18781e508460e14f64193571b98b7d)

We used a machine learning approach to evaluate plant identification potential using the hyperspectral data at multiple taxonomic resolutions: species and genus levels.

Species classification is an active research area [@scholl2020integrating].

@@

## Data cleaning

## Species classification

## Genus classification

Same setup as species classification, but used the genus as each class label.

@@

Max has cool ideas and knows many R tricks

@@

\clearpage

# Figure legends {-}

## Figure 1 {-}

Figure 1 info...

## Figure 2 {-}

It ain't much...

# Figures {-}

## Figure 1 {-}

```{r spectra, fig.cap = "", echo=FALSE,  out.width = "450px", message = FALSE, warning=FALSE}
library(here)
knitr::include_graphics(here::here("analysis", "figures", "spectra_figure_test.png"))
```

\clearpage

## Figure 2 {-}

```{r excel, fig.cap = "", echo=FALSE,  out.width = "450px", message = FALSE, warning=FALSE}
knitr::include_graphics(here::here("analysis", "figures", "honest_work.jpeg"))
```

\clearpage
